### 2015-12-02 paper.tex
Comment already existing as issue #7

We see that strut drag losses increase with tip speed ratio to the power 2--3,
which makes streamlined struts much more important for low solidity turbines,
given the inverse correlation between solidity and $\lambda_0$.\textbf{\textit{[need more to write here]}}

>>>>

We see that strut drag losses increase with tip speed ratio to the power 2--3,
which makes streamlined struts much more important for low solidity turbines,
given the inverse correlation between solidity and $\lambda_0$.
